Generating Synthetic Data

### 2022-12-23 sections/data_preprocessing/_synthetic_data.qmd
rejigged artifacts

---
title: Generating Synthetic Data
---

@@

>>>>

## Generating Synthetic Data

@@

```{julia}
#| output: true

catalogue = load_synthetic()
function plot_data(data,title)
    plt = plot(title=uppercasefirst(replace(string(title),"_" => " ")))
    scatter!(data)
    return plt
end
plts = [plot_data(data,name) for (name, data) in catalogue]
plt = plot(plts..., layout=(1,4), size=(850,200))
savefig(plt, "paper/www/synthetic_data.png")
display(plt)
```

```{julia}
generate_artifacts(data_path)
```
